---
title: "BSH Mandatory vs BSH Voluntary vs Rest of the PH households."
date: "October 23, 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r pressure, echo=FALSE}
load("/media/anirban/a84ef5e0-59cf-454d-aeae-e112c9915900/home/anirban/Documents/BHP-New/BHP-2017-roundData/combined-Oct23-2017.RData")
admin2017 <- read.csv("/media/anirban/a84ef5e0-59cf-454d-aeae-e112c9915900/home/anirban/Documents/BHP-New/BHP-2017-roundData/admin2017.csv")
admin2017 <- admin2017[!is.na(admin2017$Tenant) & admin2017$Tenant!="", ]
BSH <- read.csv("/media/anirban/a84ef5e0-59cf-454d-aeae-e112c9915900/home/anirban/Documents/BHP-New/BHP-2017-roundData/BSH_mandatoryVsVoluntary.csv", header=FALSE)
BSH_1 <- read.table("/media/anirban/a84ef5e0-59cf-454d-aeae-e112c9915900/home/anirban/Documents/BHP-New/BHP-2017-roundData/BSH-list.csv", quote="\"", comment.char="")
BSH <- BSH[-grep("t0011523", as.character(BSH$V1))[1], ]
BSH_1 <- BSH_1[-grep("t0011523", as.character(BSH_1$V1))[1], ]

final <- subset(final, !is.na(From.y))
library("ggplot2")
library("plyr")
#library("dplyr")
#library("pander")
library("reshape2")
library("scales")

mandatory <- final[final$TCode %in% BSH$V1[BSH$V2=="Mandatory"] , ]

voluntary <- final[final$TCode %in% BSH$V1[BSH$V2=="Voluntary"] , ]

restPH <- final[!(final$TCode %in% BSH$V1) , ]

```


Non-BSH group N:
```{r, echo=FALSE}
length(restPH$TCode)

```

Voluntary BSH group N:
```{r, echo=FALSE}
length(voluntary$TCode)

```

Mandatory BSH group N:
```{r, echo=FALSE}

length(mandatory$TCode)
```


```{r, echo=FALSE}
restPH$F <- "Non-BSH"
voluntary$F <- "Voluntary BSH"
mandatory$F <- "Mandatory BSH"
all <- rbind(restPH, voluntary, mandatory)
all$F <- as.factor(all$F)
#summary(all$F)


Q <- c("Q1","Q2","Q3_1","Q3_2","Q3_3","Q3_4","Q3_5","Q3_6","Q3_7","Q3_8","Q3_9","Q4","Q5","Q6","Q7","Q8_1_1","Q8_1_2","Q8_1_3","Q8_1_4","Q8_1_5","Q8_1_6","Q8_1_7","Q8_1_8","Q8_1_9","Q8_1_10","Q8_1_11","Q8_1_12","Q8_1_13","Q8_1_14","Q9","Q10_1","Q10_2","Q10_3","Q10_4","Q10_5","Q10_6","Q10_7","Q10_8","Q11","Q12","Q13_1","Q13_2","Q13_3","Q13_4","Q13_5","Q14","Q15_1","Q15_2","Q15_3","Q15_4","Q16_1","Q16_2","Q16_3","Q16_4","Q16_5","Q16_6","Q17","Q18_1","Q18_2","Q18_3","Q18_4","Q18_5","Q18_6","Q18_7","Q18_8","Q18_9","Q18_10","Q19","Q20","Q21_1","Q21_2","Q21_3","Q22_1","Q22_2","Q22_3","Q23_1","Q23_2","Q23_3","Q23_4","Q23_5","Q24_1","Q24_2","Q24_3","Q24_4","Q24_5","Q24_6","Q25_1","Q25_2","Q25_3","Q25_4","Q25_5","Q25_6","Q25_7","Q26","Q27_1","Q27_2","Q27_3","Q27_4","Q28","Q29","Q30_1","Q31","Q32","Q33","Q34","Q35_1","Q35_2","Q35_3","Q35_4","Q35_5","Q35_6","Q35_7","Q35_8","Q35_9","Q35_10","Q35_11","Q35_12","Q36_1","Q36_2","Q36_3","Q36_4","Q36_5","Q36_6","Q36_7","Q36_8","Q36_9","Q36_10","Q36_11","Q37","Q38","Q39")


admin <- c("Member.Age...as.of.date", "MemberCitizen_17", "Member.Sex", "Member.Ethnicity", "HH.Members.under.age.13", "Single.Parent.HH", "Total.Annual.Income")

```
### Age.
Member.Age...as.of.date
```{r, echo=FALSE}





all$`MemberAge-asofdate_17`[is.na(all$`MemberAge-asofdate_17`)] <- all$Member.Age...as.of.date_15[is.na(all$`MemberAge-asofdate_17`)]
Mandatory_17Median <- median(all$`MemberAge-asofdate_17`[all$F=="Mandatory BSH"], na.rm = TRUE)
Voluntary_17Median <- median(all$`MemberAge-asofdate_17`[all$F=="Voluntary BSH"], na.rm = TRUE)
rest_17Median <- median(all$`MemberAge-asofdate_17`[all$F=="Non-BSH"], na.rm = TRUE)
med <- data.frame(F=c("Mandatory BSH", "Voluntary BSH", "Non-BSH"), m=c(Mandatory_17Median, Voluntary_17Median, rest_17Median))

ggplot(all, aes(x = all$F, y = all$`MemberAge-asofdate_17`)) + 
  geom_boxplot() +
  xlab("") + ylab("Member Age in 2017") +
  geom_text(data = med, aes(x=med$F, y=med$m, label=med$m, vjust = -0.5, hjust=0.5, color = "red")) + theme(legend.position="none") +
  ggtitle("Comparison of Age as of 2017")

```


### Health questions.
Q3_4: Health issues - a barrier to SS in housing?
```{r, echo=FALSE}
for(i in c("Q3_4")) {
  x <- paste0("mandatory$", i, "_17", sep="")
  #print(c(x, length(eval(parse(text = x))[!is.na(eval(parse(text = x)))])))
  #print(summary(eval(parse(text = x)))[2]/(length(eval(parse(text = x))[!is.na(eval(parse(text = x)))])))
  x <- paste0("mandatory$", i, "_17", sep="")
  #print(c(x, length(eval(parse(text = x))[!is.na(eval(parse(text = x)))])))
  #print(summary(eval(parse(text = x)))[2]/(length(eval(parse(text = x))[!is.na(eval(parse(text = x)))])))
  x <- paste0("voluntary$", i, "_17", sep="")
  #print(c(x, length(eval(parse(text = x))[!is.na(eval(parse(text = x)))])))
  #print(summary(eval(parse(text = x)))[2]/(length(eval(parse(text = x))[!is.na(eval(parse(text = x)))])))
  temp <- data.frame(a = c("Mandatory BSH", "Non-BSH", "Voluntary BSH"), N=c(NA, NA, NA), PercentYes=c(NA, NA, NA))
  x <- paste0("mandatory$", i, "_17", sep="")
  temp$N[1] <- length(eval(parse(text = x))[!is.na(eval(parse(text = x)))])
  temp$PercentYes[1] <- 100*(summary(eval(parse(text = x)))[2]/(length(eval(parse(text = x))[!is.na(eval(parse(text = x)))])))
  x <- paste0("restPH$", i, "_17", sep="")
  temp$N[2] <- length(eval(parse(text = x))[!is.na(eval(parse(text = x)))])
  temp$PercentYes[2] <- 100*(summary(eval(parse(text = x)))[2]/(length(eval(parse(text = x))[!is.na(eval(parse(text = x)))])))
  x <- paste0("voluntary$", i, "_17", sep="")
  temp$N[3] <- length(eval(parse(text = x))[!is.na(eval(parse(text = x)))])
  temp$PercentYes[3] <- 100*(summary(eval(parse(text = x)))[2]/(length(eval(parse(text = x))[!is.na(eval(parse(text = x)))])))
  
}

ggplot(temp, aes(x=temp$a, y=(temp$PercentYes))) + geom_bar(stat="identity", fill="red", alpha=0.25) + 
  geom_text(aes(x=temp$a, y=(temp$PercentYes), label=paste(as.character(round(temp$PercentYes)), " (N = ", as.character(temp$N), ")", sep="")), vjust = "inward") + 
  xlab("") + ylab("Percent Yes") +
  ggtitle("Q3_4: Health issues barrier to SS in housing?\n")


  
```


Q8_2:	Health problems - a barrier to employment?
```{r, echo=FALSE}

temp <- data.frame(a = c("Mandatory BSH", "Non-BSH", "Voluntary BSH"), N=c(NA, NA, NA), PercentYes=c(NA, NA, NA))
i <- "Q8_2"

x <- paste0("mandatory$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[1] <- length(x[!is.na(x)])
temp$PercentYes[1] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

x <- paste0("restPH$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[2] <- length(x[!is.na(x)])
temp$PercentYes[2] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

x <- paste0("voluntary$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[3] <- length(x[!is.na(x)])
temp$PercentYes[3] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

ggplot(temp, aes(x=temp$a, y=(temp$PercentYes))) + geom_bar(stat="identity", fill="red", alpha=0.25) + 
  geom_text(aes(x=temp$a, y=(temp$PercentYes), label=paste(as.character(round(temp$PercentYes)), " (N = ", as.character(temp$N), ")", sep="")), vjust = "inward") + 
  xlab("") + ylab("Percent Yes") +
  ggtitle("Q8_2:	Health problems - a barrier to employment?\n")


```

Q10_3: Very hard to pay for... health care for myself and my family?
```{r, echo=FALSE}

temp <- data.frame(a = c("Mandatory BSH", "Non-BSH", "Voluntary BSH"), N=c(NA, NA, NA), PercentYes=c(NA, NA, NA))
i <- "Q10_3"

x <- paste0("mandatory$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[1] <- length(x[!is.na(x)])
temp$PercentYes[1] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

x <- paste0("restPH$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[2] <- length(x[!is.na(x)])
temp$PercentYes[2] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

x <- paste0("voluntary$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[3] <- length(x[!is.na(x)])
temp$PercentYes[3] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

ggplot(temp, aes(x=temp$a, y=(temp$PercentYes))) + geom_bar(stat="identity", fill="red", alpha=0.25) + 
  geom_text(aes(x=temp$a, y=(temp$PercentYes), label=paste(as.character(round(temp$PercentYes)), " (N = ", as.character(temp$N), ")", sep="")), vjust = "inward") + 
  xlab("") + ylab("Percent Yes") +
  ggtitle("Q10_3: Very hard to pay for\nhealth care for myself and my family?\n")


```

Q18_2: Personal or family members’ health - a barrier to transportation?
```{r, echo=FALSE}

temp <- data.frame(a = c("Mandatory BSH", "Non-BSH", "Voluntary BSH"), N=c(NA, NA, NA), PercentYes=c(NA, NA, NA))
i <- "Q18_2"

x <- paste0("mandatory$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[1] <- length(x[!is.na(x)])
temp$PercentYes[1] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

x <- paste0("restPH$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[2] <- length(x[!is.na(x)])
temp$PercentYes[2] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

x <- paste0("voluntary$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[3] <- length(x[!is.na(x)])
temp$PercentYes[3] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

ggplot(temp, aes(x=temp$a, y=(temp$PercentYes))) + geom_bar(stat="identity", fill="red", alpha=0.25) + 
  geom_text(aes(x=temp$a, y=(temp$PercentYes), label=paste(as.character(round(temp$PercentYes)), " (N = ", as.character(temp$N), ")", sep="")), vjust = "inward") + 
  xlab("") + ylab("Percent Yes") +
  ggtitle("Q18_2: Personal or family members’ health\na barrier to transportation?\n")

```


Q29: How would you rate your current health?
```{r, echo=FALSE}

temp <- data.frame(a = c("Mandatory BSH", "Non-BSH", "Voluntary BSH"), N=c(NA, NA, NA), PercentYes=c(NA, NA, NA))
i <- "Q29"

x <- paste0("mandatory$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[1] <- length(x[!is.na(x)])
temp$PercentYes[1] <- 100*((summary(x)[1] + summary(x)[2])/(length(x[!is.na(x)])))

x <- paste0("restPH$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[2] <- length(x[!is.na(x)])
temp$PercentYes[2] <- 100*((summary(x)[1] + summary(x)[2])/(length(x[!is.na(x)])))

x <- paste0("voluntary$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[3] <- length(x[!is.na(x)])
temp$PercentYes[3] <- 100*((summary(x)[1] + summary(x)[2])/(length(x[!is.na(x)])))

ggplot(temp, aes(x=temp$a, y=(temp$PercentYes))) + geom_bar(stat="identity", fill="red", alpha=0.25) + 
  geom_text(aes(x=temp$a, y=(temp$PercentYes), label=paste(as.character(round(temp$PercentYes)), " (N = ", as.character(temp$N), ")", sep="")), vjust = "inward") + 
  xlab("") + ylab("Percent who reported Poor or Quite Poor") +
  ggtitle("Q29: How would you rate your current health?\n")

```

Q35_11:	Health issues - a barrier to education?
```{r, echo=FALSE}

temp <- data.frame(a = c("Mandatory BSH", "Non-BSH", "Voluntary BSH"), N=c(NA, NA, NA), PercentYes=c(NA, NA, NA))
i <- "Q35_11"

x <- paste0("mandatory$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[1] <- length(x[!is.na(x)])
temp$PercentYes[1] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

x <- paste0("restPH$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[2] <- length(x[!is.na(x)])
temp$PercentYes[2] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

x <- paste0("voluntary$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[3] <- length(x[!is.na(x)])
temp$PercentYes[3] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

ggplot(temp, aes(x=temp$a, y=(temp$PercentYes))) + geom_bar(stat="identity", fill="red", alpha=0.25) + 
  geom_text(aes(x=temp$a, y=(temp$PercentYes), label=paste(as.character(round(temp$PercentYes)), " (N = ", as.character(temp$N), ")", sep="")), vjust = "inward") + 
  xlab("") + ylab("Percent Yes") +
  ggtitle("Q35_11:	Health issues - a barrier to education?\n")
```

Q36_9: Health Self Assessment
```{r, echo=FALSE}

temp <- data.frame(a = c("Mandatory BSH", "Non-BSH", "Voluntary BSH"), N=c(NA, NA, NA), PercentYes=c(NA, NA, NA))
i <- "Q36_9"

x <- paste0("mandatory$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[1] <- length(x[!is.na(x)])
temp$PercentYes[1] <- 100*((summary(x)[1] + summary(x)[2])/(length(x[!is.na(x)])))

x <- paste0("restPH$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[2] <- length(x[!is.na(x)])
temp$PercentYes[2] <- 100*((summary(x)[1] + summary(x)[2])/(length(x[!is.na(x)])))

x <- paste0("voluntary$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[3] <- length(x[!is.na(x)])
temp$PercentYes[3] <- 100*((summary(x)[1] + summary(x)[2])/(length(x[!is.na(x)])))

ggplot(temp, aes(x=temp$a, y=(temp$PercentYes))) + geom_bar(stat="identity", fill="red", alpha=0.25) + 
  geom_text(aes(x=temp$a, y=(temp$PercentYes), label=paste(as.character(round(temp$PercentYes)), " (N = ", as.character(temp$N), ")", sep="")), vjust = "inward") + 
  xlab("") + ylab("Percent who reported\nsituation is Urgent or Vulnerable") +
  ggtitle("Q36_9: Health Self Assessment\n")


```

### Employment
Q3_1: Not having a paying job - barrier to SS in housing
```{r, echo=FALSE}
temp <- data.frame(a = c("Mandatory BSH", "Non-BSH", "Voluntary BSH"), N=c(NA, NA, NA), PercentYes=c(NA, NA, NA))
i <- "Q3_1"

x <- paste0("mandatory$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[1] <- length(x[!is.na(x)])
temp$PercentYes[1] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

x <- paste0("restPH$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[2] <- length(x[!is.na(x)])
temp$PercentYes[2] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

x <- paste0("voluntary$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[3] <- length(x[!is.na(x)])
temp$PercentYes[3] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

ggplot(temp, aes(x=temp$a, y=(temp$PercentYes))) + geom_bar(stat="identity", fill="red", alpha=0.25) + 
  geom_text(aes(x=temp$a, y=(temp$PercentYes), label=paste(as.character(round(temp$PercentYes)), " (N = ", as.character(temp$N), ")", sep="")), vjust = "inward") + 
  xlab("") + ylab("Percent Yes") +
  ggtitle("Q3_1: Not having a paying job\na barrier to SS in housing\n")
```


Q8_3: Lack of education or skills - a barrier to employment?
```{r, echo=FALSE}
temp <- data.frame(a = c("Mandatory BSH", "Non-BSH", "Voluntary BSH"), N=c(NA, NA, NA), PercentYes=c(NA, NA, NA))
i <- "Q8_3"

x <- paste0("mandatory$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[1] <- length(x[!is.na(x)])
temp$PercentYes[1] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

x <- paste0("restPH$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[2] <- length(x[!is.na(x)])
temp$PercentYes[2] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

x <- paste0("voluntary$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[3] <- length(x[!is.na(x)])
temp$PercentYes[3] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

ggplot(temp, aes(x=temp$a, y=(temp$PercentYes))) + geom_bar(stat="identity", fill="red", alpha=0.25) + 
  geom_text(aes(x=temp$a, y=(temp$PercentYes), label=paste(as.character(round(temp$PercentYes)), " (N = ", as.character(temp$N), ")", sep="")), vjust = "inward") + 
  xlab("") + ylab("Percent Yes") +
  ggtitle("Q8_3: Lack of education or skills\na barrier to employment?\n")
```

Q5	Employment Status
```{r, echo=FALSE}


temp <- data.frame(a = c("Mandatory BSH", "Non-BSH", "Voluntary BSH"), N=c(NA, NA, NA), PercentYes=c(NA, NA, NA))
i <- "Q5"

x <- paste0("mandatory$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[1] <- length(x[!is.na(x)])
temp$PercentYes[1] <- 100*((summary(x)[1] + summary(x)[2])/(length(x[!is.na(x)])))

x <- paste0("restPH$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[2] <- length(x[!is.na(x)])
temp$PercentYes[2] <- 100*((summary(x)[1] + summary(x)[2])/(length(x[!is.na(x)])))

x <- paste0("voluntary$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[3] <- length(x[!is.na(x)])
temp$PercentYes[3] <- 100*((summary(x)[1] + summary(x)[2])/(length(x[!is.na(x)])))

ggplot(temp, aes(x=temp$a, y=(temp$PercentYes))) + geom_bar(stat="identity", fill="red", alpha=0.25) + 
  geom_text(aes(x=temp$a, y=(temp$PercentYes), label=paste(as.character(round(temp$PercentYes)), " (N = ", as.character(temp$N), ")", sep="")), vjust = "inward") + 
  xlab("") + ylab("Percent who reported\nemployed year-round full- or part-time") +
  ggtitle("Q5	Employment Status\n")

```

Q36_2	Employment Self Assessment
```{r, echo=FALSE}

temp <- data.frame(a = c("Mandatory BSH", "Non-BSH", "Voluntary BSH"), N=c(NA, NA, NA), PercentYes=c(NA, NA, NA))
i <- "Q36_2"

x <- paste0("mandatory$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[1] <- length(x[!is.na(x)])
temp$PercentYes[1] <- 100*((summary(x)[1] + summary(x)[2])/(length(x[!is.na(x)])))

x <- paste0("restPH$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[2] <- length(x[!is.na(x)])
temp$PercentYes[2] <- 100*((summary(x)[1] + summary(x)[2])/(length(x[!is.na(x)])))

x <- paste0("voluntary$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[3] <- length(x[!is.na(x)])
temp$PercentYes[3] <- 100*((summary(x)[1] + summary(x)[2])/(length(x[!is.na(x)])))

ggplot(temp, aes(x=temp$a, y=(temp$PercentYes))) + geom_bar(stat="identity", fill="red", alpha=0.25) + 
  geom_text(aes(x=temp$a, y=(temp$PercentYes), label=paste(as.character(round(temp$PercentYes)), " (N = ", as.character(temp$N), ")", sep="")), vjust = "inward") + 
  xlab("") + ylab("Percent who reported\nsituation is Urgent or Vulnerable") +
  ggtitle("Q36_2	Employment Self Assessment\n")
```

### Immigration questions
Q8_15: Immigration status - a barrier to SS in employment
```{r, echo=FALSE}


temp <- data.frame(a = c("Mandatory BSH", "Non-BSH", "Voluntary BSH"), N=c(NA, NA, NA), PercentYes=c(NA, NA, NA))
i <- "Q8_14"

x <- paste0("mandatory$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[1] <- length(x[!is.na(x)])
temp$PercentYes[1] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

x <- paste0("restPH$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[2] <- length(x[!is.na(x)])
temp$PercentYes[2] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

x <- paste0("voluntary$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[3] <- length(x[!is.na(x)])
temp$PercentYes[3] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

ggplot(temp, aes(x=temp$a, y=(temp$PercentYes))) + geom_bar(stat="identity", fill="red", alpha=0.25) + 
  geom_text(aes(x=temp$a, y=(temp$PercentYes), label=paste(as.character(round(temp$PercentYes)), " (N = ", as.character(temp$N), ")", sep="")), vjust = "inward") + 
  xlab("") + ylab("Percent Yes") +
  ggtitle("Q8_15: Immigration status\na barrier to SS in employment?\n")

```

Q35_12: Immigration Status - a barrier to advance your education/skills?
```{r, echo=FALSE}
temp <- data.frame(a = c("Mandatory BSH", "Non-BSH", "Voluntary BSH"), N=c(NA, NA, NA), PercentYes=c(NA, NA, NA))
i <- "Q35_12"

x <- paste0("mandatory$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[1] <- length(x[!is.na(x)])
temp$PercentYes[1] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

x <- paste0("restPH$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[2] <- length(x[!is.na(x)])
temp$PercentYes[2] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

x <- paste0("voluntary$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[3] <- length(x[!is.na(x)])
temp$PercentYes[3] <- 100*(summary(x)[2]/(length(x[!is.na(x)])))

ggplot(temp, aes(x=temp$a, y=(temp$PercentYes))) + geom_bar(stat="identity", fill="red", alpha=0.25) + 
  geom_text(aes(x=temp$a, y=(temp$PercentYes), label=paste(as.character(round(temp$PercentYes)), " (N = ", as.character(temp$N), ")", sep="")), vjust = "inward") + 
  xlab("") + ylab("Percent Yes") +
  ggtitle("Q35_12: Immigration Status\n a barrier to advance your education/skills?\n")
```

Q36_11: Self Assessment of SS in immigration status
```{r, echo=FALSE, fig.height=5}

temp <- data.frame(a = c("Mandatory BSH", "Non-BSH", "Voluntary BSH"), N=c(NA, NA, NA), PercentYes=c(NA, NA, NA))
i <- "Q36_11"

x <- paste0("mandatory$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[1] <- length(x[!is.na(x)])
temp$PercentYes[1] <- 100*((summary(x)[1] + summary(x)[2])/(length(x[!is.na(x)])))

x <- paste0("restPH$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[2] <- length(x[!is.na(x)])
temp$PercentYes[2] <- 100*((summary(x)[1] + summary(x)[2])/(length(x[!is.na(x)])))

x <- paste0("voluntary$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[3] <- length(x[!is.na(x)])
temp$PercentYes[3] <- 100*((summary(x)[1] + summary(x)[2])/(length(x[!is.na(x)])))

ggplot(temp, aes(x=temp$a, y=(temp$PercentYes))) + geom_bar(stat="identity", fill="red", alpha=0.25) + 
  geom_text(aes(x=temp$a, y=(temp$PercentYes), label=paste(as.character(round(temp$PercentYes)), " (N = ", as.character(temp$N), ")", sep="")), vjust = "inward") + 
  xlab("") + ylab("Percent who reported\nsituation is Urgent or Vulnerable") +
  ggtitle("Q36_11: Self Assessment of SS in immigration status\n")

```

Member.Citizen
```{r, echo=FALSE}

temp <- data.frame(a = c("Mandatory BSH", "Non-BSH", "Voluntary BSH"), N=c(NA, NA, NA), PercentYes=c(NA, NA, NA))
i <- "MemberCitizen_17"

x <- paste0("as.factor(mandatory$", i, "_17)", sep="")
x <- eval(parse(text = x))
temp$N[1] <- length(x)
temp$PercentYes[1] <- 100*(as.numeric(summary(as.factor(mandatory$MemberCitizen_17))[1]) + as.numeric(summary(as.factor(mandatory$MemberCitizen_17))[2]))/length((as.factor(mandatory$MemberCitizen_17)))

x <- paste0("as.factor(restPH$", i, "_17)", sep="")
x <- eval(parse(text = x))
temp$N[2] <- length(x)
temp$PercentYes[2] <- 100*(as.numeric(summary(as.factor(restPH$MemberCitizen_17))[1]) + as.numeric(summary(as.factor(restPH$MemberCitizen_17))[2]))/length((as.factor(restPH$MemberCitizen_17)))

x <- paste0("as.factor(voluntary$", i, "_17)", sep="")
x <- eval(parse(text = x))
temp$N[3] <- length(x)
temp$PercentYes[3] <- 100*(as.numeric(summary(as.factor(voluntary$MemberCitizen_17))[1]) + as.numeric(summary(as.factor(voluntary$MemberCitizen_17))[2]))/length((as.factor(voluntary$MemberCitizen_17)))


ggplot(temp, aes(x=temp$a, y=(temp$PercentYes))) + geom_bar(stat="identity", fill="red", alpha=0.25) + 
  geom_text(aes(x=temp$a, y=(temp$PercentYes), label=paste(as.character(round(temp$PercentYes)), " (N = ", as.character(temp$N), ")", sep="")), vjust = "inward") + 
  xlab("") + ylab("Percent who reported\nEligible Citizen or Eligible Non-Citizen") +
  ggtitle("Citizenship based on BHP administrative data\n")


```

### Total annual income

```{r, echo=FALSE}

#all <- subset(all, F!="Voluntary BSH" & !is.na(TotalAnnualIncome_17))
mandatory_2017_N <- length(all$TotalAnnualIncome_17[all$F=="Mandatory BSH"])
restPH_2017_N <- length(all$TotalAnnualIncome_17[all$F=="Non-BSH"])
voluntary_2017_N <- length(all$TotalAnnualIncome_17[all$F=="Voluntary BSH"])
mandatory17Median <- median(all$TotalAnnualIncome_17[all$F=="Mandatory BSH"])
restPH17Median <- median(all$TotalAnnualIncome_17[all$F=="Non-BSH"])
voluntary17Median <- median(all$TotalAnnualIncome_17[all$F=="Voluntary BSH"])
temp <- data.frame(F = c("Mandatory BSH", "Non-BSH", "Voluntary BSH"), 
                  # N=c(mandatory_2017_N, restPH_2017_N, voluntary_2017_N), 
                   m=c(mandatory17Median, restPH17Median, voluntary17Median))

ggplot(all, aes(x = all$F, y = all$TotalAnnualIncome_17)) + 
  geom_boxplot() +
  xlab("") + ylab("Total annual income in 2017") +
  geom_text(data = temp, aes(x=temp$F, y=temp$m, label=temp$m, vjust = -0.5, hjust=0.5, color = "red")) + theme(legend.position="none") +
  ggtitle(paste0("Comparison of Income as of 2017", sep = ""))

  

```


Q9: Income ran out last three months?
```{r, echo=FALSE}

temp <- data.frame(a = c("Mandatory BSH", "Non-BSH", "Voluntary BSH"), N=c(NA, NA, NA), PercentYes=c(NA, NA, NA))
i <- "Q9"

x <- paste0("mandatory$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[1] <- length(x[!is.na(x)])
temp$PercentYes[1] <- 100*(summary(x)[1]/(length(x[!is.na(x)])))

x <- paste0("restPH$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[2] <- length(x[!is.na(x)])
temp$PercentYes[2] <- 100*(summary(x)[1]/(length(x[!is.na(x)])))

x <- paste0("voluntary$", i, "_17", sep="")
x <- eval(parse(text = x))
temp$N[3] <- length(x[!is.na(x)])
temp$PercentYes[3] <- 100*(summary(x)[1]/(length(x[!is.na(x)])))

ggplot(temp, aes(x=temp$a, y=(temp$PercentYes))) + geom_bar(stat="identity", fill="red", alpha=0.25) + 
  geom_text(aes(x=temp$a, y=(temp$PercentYes), label=paste(as.character(round(temp$PercentYes)), " (N = ", as.character(temp$N), ")", sep="")), vjust = "inward") + 
  xlab("") + ylab("Percent who reported Never") +
  ggtitle("Q9: Income ran out last three months?\n")


```


